\documentclass[12pt, a4]{article}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[greek, english]{babel}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\usepackage{geometry}

\begin{document}

\newgeometry{left=0.8in,right=0.8in,top=1in,bottom=1in}
\noindent \rule{\textwidth}{3pt}
\begin{center}
	{\bf \Large{Milestone 1 Report}}\\
	ACE411-Embedded Microprocessor Systems \\
	Winter semester of academic year 2021-2022
	\rule{\textwidth}{0.2mm} 
	\begin{tabular}{l r}
		Kallinteris Andreas:& 2017030066 \\ 
		Lioudakis Emmanouil:      &2018030020 
	\end{tabular} \vrule \hspace{3mm}
	\indent	Team number on eclass:  5
	\rule{\textwidth}{1pt}
\end{center}

\section*{STK500 configuration}
The STK500 development board we have received has installed the ATmega16L microcontroller, which is fully compatible with the ATmega16 used in Microchip Studio. PORTA is fully functional, and therefore connected to the LEDs. Since ISP (In System Programmer) programming mode is used, the following jumpers are set:



\section*{Microchip configuration - Compilation process}
Since the code is written using the C++ language (using newer standards than the supported from Microchip Studio), some modifications should be done to the default settings of a new C++ project.  \\
Firstly, add the symbol “AVR” to the compiler’s symbols:\\
IMAGE 1\\
Secondly, add the flag “-std=c++17” to the compiler’s flags:\\
IMAGE 2\\
The optimization level should be set to “-O2 (Optimize more).\\
Finally, the SIMULATION\_MODE should be defined (by uncommenting the line 25 of main.cpp). When it is defined, the program will read from TCNT2 instead of UDR and will redi-rect its output from UDR to TCNT0. By doing that, the program can be simulated with the provided stimuli files.

\section*{Description of the program}

\subsubsection*{The sudoku solving algorithm}
TO BE COMPLETED BY ANDREAS

\subsubsection*{Controlling the LED progress bar}
To update the LEDs that show the progress of solving, there were two options. The first one was updating the PORTA register every time we change the value of a cell and the second one was refreshing the LEDs with a 30Hz frequency. The former option would consume many clock cycles (because on every PORTA update, its new value is read from flash, which needs 3 clock cycles and), when the latter would consume those 3 cycles only 30 times per second, which is pleasant for the human eye. So, the latter was used by enabling Timer/Counter1 and using its Output Compare Match Interrupt. The interrupt is fired with a 30Hz frequency and it simply updates the value of PORTA.

\subsubsection*{UART}
by elioudakis

\section*{Resource usage}
\subsubsection*{Program memory (flash)}

\subsubsection*{Static RAM (SRAM)}

\section*{Simulation in Microchip Studio, using stimuli files}
X stimuli files are submitted with the code:
\begin{itemize}
\item	a, which feeds the program with one sudoku board (the one shown in the assign-ment), waits until the sudoku is solved and sends the results back.
\item	a, which feeds the program with the same sudoku board as above, but while solving, a “break” command stops the solving process, and using the “debug” command, the contents of some cells are read.
\item	a, which feeds the program with two sudoku boards, one after another. After solving the first and sending back the results, a “clear” command is executed and then the grid is filled with the second sudoku, it is solved and the results are sent back to the serial port.
\end{itemize}

\section*{Testing the code on real hardware (STK500)}
\subsubsection*{Using PuTTY}
\subsubsection*{Using the interface program developed by Odysseas Stavrou}


\end{document}